Automatic Generation of Knowledge Representation

### 2012-12-27 ontologies/paper.tex
added initial structure to ontologies paper and bib files

%\documentclass[4pt,a4paper]{article}
\documentclass[4pt,a4paper,twocolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{algorithm}
\usepackage{textcomp}
\usepackage{fontenc}
\usepackage{tipa}
\usepackage{framed}
\usepackage{multicol}
\usepackage{color}
\usepackage{qtree}
\usepackage{graphicx}
\usepackage{amsmath}

@@

\section{Problem}
In the given paper [1] the authors describe a method for automatically creating a taxonomy.
The domain of the problem are the issues of a Callcenter. The Call center handles user problems related to different sofware and services.
The proposed method use  written and speech records between the agents of the call center and the clients. 
In the next sections  the method for transforming unstructured data into a knowledge representation proposed by the paper will be described,
then a critical review and opinion over the method will be given. Addionally a comparison between the given paper and other papers willing to automatically construct knowledge representation is made.
The last section covers  possible applications of automatically constructed Ontologies in hte domain of Natural Language Processing.

@@

Automatically creating knowledge representation from unstructured text has been a focus of study given the amount of data available in the web.
Projects such as 'Know it all'[2] considers the problem of developing a variety of domain-independent systems that extract information from the Web in an autonomous, scalable way.Google for example has the project 'The knowledge Graph' which considers the automatically construction of an ontology by using the web knowledge.

@@

[1] exposition paper
[2] http://www.cs.washington.edu/research/knowitall/

>>>>

%\documentclass[4pt,a4paper]{article}
\documentclass[4pt,a4paper,twocolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{algorithm}
\usepackage{textcomp}
\usepackage{fontenc}
\usepackage{tipa}
\usepackage{framed}
\usepackage{multicol}
\usepackage{color}
\usepackage{graphicx}
\usepackage{amsmath}

@@

\section{Problem}
In the given paper ~\cite{Roy:2006:AGD:1220175.1220268} the authors describe a method for automatically creating a taxonomy.
The domain of the problem are the issues of a Callcenter. The Call center handles user problems related to different sofware and services.
The proposed method use  written and speech records between the agents of the call center and the clients. 
In the next sections  the method for transforming unstructured data into a knowledge representation proposed by the paper will be described,
then a critical review and opinion over the method will be given. Addionally a comparison between the given paper and other papers willing to automatically construct knowledge representation is made.
The last section covers  possible applications of automatically constructed Ontologies in hte domain of Natural Language Processing.

@@

Automatically creating knowledge representation from unstructured text has been a focus of study given the amount of data available in the web.
Projects such as 'Know it all'\footnote{\url{http://www.cs.washington.edu/research/knowitall/}} considers the problem of developing a variety of domain-independent systems that extract information from the Web in an autonomous, scalable way.Google for example has the project 'The knowledge Graph' which considers the automatically construction of an ontology by using the web knowledge.

@@
